Conceptual and methodological problems with bias detection and avoidance in natural language processing

### 2021-06-19 thesis/04-discussion.Rmd
Adds files

@@

# Summary

The aim of this paper was to show the analysis of bias detection methods used in modern natural language processing projects.

In the further research it is worth to dive deeper into some issues or to examine new ideas that occurred during our work.

>>>>

1. Our proposition - Bayesian method (red) comment on remarks from chapter2 and then; what we do better
- general insights - estimeated coefficients mean - general HPDI and general different similar - after debiasing the same almost for reddit
- details from the words view - questions: analyzing table features; when human slightly closer - unexpected;
describe the features; 3 small csvs; reddit, google reddit-debiased;general human moved closer- not in table but in sentences; 
comments and values that refer to them: (blue and green)
a) google scale
b) associated females
debiased: question about the change
- better but not for muslims
- corpus frequency maybe?
- better for male
- when in gender different and associated together maybe it is better - gender is very specific, words are about professions; 
- when in religion it is bad different and associated
-  in race it is not obvious - mixed sentiments

black remarks then:
- mess, change protected words; relative differences stay the same, by the way lipstick on a pig
- word lists are strange, not enough words, large HPDI

4. Summary (how abstract ends)

@@
